Thermodynamic fragments in magic state theories

### 2021-01-21 magic_paper.tex
Full n-copy first elbow coordinates. Need to expand on the first elbow constraint

As illustrated in~\cref{tab:thermal_w}, the phase space can be split into three regions, based on the different values of the slope $\widetilde{\bmw}$.
As more copies ($n>1$) are considered, the system is described by higher dimensional phase spaces which contains more regions of different slope.
Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
\begin{equation}
	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}[\bmx]}{\W{\gamma\too{n}}[\bmx]} = \left( \frac{\W{\noisys}[\bmx]}{\W{\gamma}[\bmx]} \right)\too{n} = \widetilde{\bmw}\too{n}.
\end{equation}
Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
The process is outlined below.

According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}[\bmx]$ and $\W{\gamma\too{n}}[\bmx]$.

To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}[\bmx], \W{\gamma\too{n}}[\bmx]$, we can construct trinomial generating functions.
In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
\begin{align}
	&G(X,Y; \noisys) \coloneqq (-\nu + 5\chi X + 3\chi Y)^n \nonumber\\
	&= \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} \big] X^i Y^j, \\
	&G(X,Y; \gamma) \coloneqq \left( \frac{1}{3Z} + 5\frac{1}{3Z} X + 3 \frac{e^{-\beta}}{3Z} Y \right)^n \nonumber\\
	&= (3Z)^{-n} \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} e^{-j\beta} X^i Y^j, \\
	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3Z(-\nu) + 5(3Z\chi) X + 3(3Z\chi) e^\beta Y \Big)^n \nonumber\\
	&= (3Z)^n \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \big] X^i Y^j,
\end{align}
where the $(i,j)$-th term multiplicity $m_{ij}$ is given by
\begin{equation}
	m_{ij} \coloneqq \frac{n!}{i!j!(n-i-j)!} 5^i 3^j.
\end{equation}
There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms. 
Each term $X^i Y^j$ represents a phase space region with different slope. 
Consider the generating function $G(X,Y;\widetilde{\bmw})$ for the slope. 
The coefficient in front of the term is a product of the multiplicity $m_{ij}$ and the value of the slope in the region, $(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta}$.
To find the value of the Wigner components $\W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$ in this phase space region, we simply read the coefficients of the term $X^i Y^j$ in functions $G(X,Y; \noisys), G(X,Y; \gamma)$ respectively.

@@

We want to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$.
To do this, we first need to find the highest slope value, i.e. find
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}}.
\end{equation}
For even $n$,
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = \max{\{ \nu^n, \chi^n e^{n\beta} \}}.
\end{equation}
The final optimisation depends on the temperature regime, we work in.
Specifically, $\widetilde{\bmw}_{\rm{max}} =  \nu^n$ for
\begin{equation}\label{eq:temp_regime}
	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
\end{equation}
This value of slope corresponds to term $X^0Y^0 = 1$, so the Lorenz curve coordinates are
\begin{equation}
	(x_0, L_0) = \Big( (3Z)^{-n}, \nu^n \Big).
\end{equation}

>>>>

As illustrated in~\cref{tab:thermal_w}, the phase space can be split into three regions, based on the different values of the slope $\widetilde{\bmw}$.
As more copies ($n>1$) are considered, the system is described by higher dimensional phase spaces which contains more regions of different slope.
Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
\begin{equation}
	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} = \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
\end{equation}
Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
The process is outlined below.

According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}(\bmx)$ and $\W{\gamma\too{n}}(\bmx)$.

To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$, we can construct trinomial generating functions.
In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
\begin{align}
	&G(X,Y; \noisys) \coloneqq (-\nu + 5\chi X + 3\chi Y)^n \nonumber\\
	&= \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} \big] X^i Y^j, \\
	&G(X,Y; \gamma) \coloneqq \left( \frac{1}{3Z} + 5\frac{1}{3Z} X + 3 \frac{e^{-\beta}}{3Z} Y \right)^n \nonumber\\
	&= (3Z)^{-n} \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} e^{-j\beta} X^i Y^j, \\
	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3Z(-\nu) + 5(3Z\chi) X + 3(3Z\chi) e^\beta Y \Big)^n \nonumber\\
	&= (3Z)^n \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \big] X^i Y^j,
\end{align}
where the $(i,j)$-th term multiplicity $m_{ij}$ is given by
\begin{equation}
	m_{ij} \coloneqq \frac{n!}{i!j!(n-i-j)!} 5^i 3^j.
\end{equation}
There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms. 
Each term $X^i Y^j$ represents a phase space region with different slope. 
Consider the generating function $G(X,Y;\widetilde{\bmw})$ for the slope. 
The coefficient in front of the term is a product of the multiplicity $m_{ij}$ and the value of the slope in the region, $(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta}$.
To find the value of the Wigner components $\W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$ in this phase space region, we simply read the coefficients of the term $X^i Y^j$ in functions $G(X,Y; \noisys), G(X,Y; \gamma)$ respectively.

@@

In order to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we need to find the highest slope value,
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}},
\end{equation}
where we have ignored the positive prefactor $(3Z)^n$.
We can narrow down the maximisation, by noticing that we always have $\chi e^\beta \geq \chi$, so the maximum is achieved for $i=0$ and we can maximise over $\{ (-\nu)^{n-j} \chi^{j} e^{j\beta} \}$.
Then, notice that either $\nu \geq \chi e^{\beta}$ or $\nu < \chi e^{\beta}$, so, for even $n$, the maximum can only be achieved for $j\in\{0,n\}$ and
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = 
	\begin{cases}
		\nu^n, &\nu \geq \chi e^{\beta}, \\
		\chi^n e^{n\beta}, &\nu < \chi e^{\beta}.
	\end{cases}
\end{equation}
By expanding $\nu, \chi$, this expression can be equivalently recast in terms of a temperature regime,
\begin{equation}\label{eq:temp_regime}
	\widetilde{\bmw}_{\rm{max}} = 
	\begin{cases}
		\nu^n, &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
		\chi^n e^{n\beta}, &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
	\end{cases}
\end{equation}
The values of the slope correspond to terms $X^0Y^0 = 1$ and $X^0Y^n = Y^n$ respectively, so the Lorenz curve coordinates are
\begin{equation}
	(x_0, L_0) = 
	\begin{cases}
		\Big( (3Z)^{-n}, \nu^n \Big), &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
		\Big( \frac{e^{-n\beta}}{Z^n}, 3^n\chi^n \Big), &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
	\end{cases}
\end{equation}

Note that as $\beta$ tends to $0$, we get the first elbow coordinates that we found for the unital fragment, $(9^{-n}, \nu^n)$.
